Selective stock enhancement undermines community stability

### 2022-01-22 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@

```{r table_set1}

@@

table_legend <- "Median estimates and standard errors (SEs) are shown. Pr(> 0) and Pr(< 0) represent the proportion of parameter estimates (MCMC samples) being positive and negative, respectively (i.e., posterior probability)."

table_reg <- NULL

>>>>

source(here::here("code/table_stvy_analysis.R"))

@@

```{r table_sensitivity, results="asis"}

conditional_text <- c("whole community",
                      "enhanced species",
                      "unenhanced species")

table_sense <- knit_chunk <- NULL

for(i in 1:length(table_stvy)) {

  table_legend <- paste0("Sensitivity analysis of the community simulation. Parameter estimates of linear regression models (standard errors in parenthesis) are shown. Response variables are the effects of stock enhancement on temporal mean density ($\\mu$) and SD ($\\sigma$) of ", conditional_text[i],". Explanatory variables (i.e., simulation parameters) were standardized to a mean of zero and a standard deviation of one prior to the analysis.")

  knit_chunk <- paste0("## Table S", i, " Sensitivity analysis (", conditional_text[i],") \n",
                       table_legend,
                       "\n```{r table_s", i,", results='asis'}
                       \n\n
                       cat(table_stvy[[", i,"]], sep = '\n')
                       \n\n
                       ```\n",
                       "\n\\pagebreak\n")

  table_sense <- c(table_sense, knit_chunk)

}

`r paste(knit(text = table_sense), collapse = '\n')`

```{r table_reg}

@@

table_legend <- "Median estimates and standard errors (SEs) are shown. Pr(> 0) and Pr(< 0) represent the proportion of positive and negative estimates (MCMC samples), respectively (i.e., posterior probability)."

table_reg <- knit_chunk <- NULL
